SNEAP2021 Figures

### 2021-05-01 doc/SNEAP2021/SNEAP2021_figures.Rmd
Add dual bellows results. Add open split blanks fig.

@@

```{r}
dfc
```

>>>>

```{r}
data <- get_hgis_data(here("data/USAMS052318RHIGS.txt")) %>% 
                  mutate(Num = ifelse(Pos == 15, "S", "U"))
stdrat <- mean(data$cor1412he[data$Num == "S" & data$outlier == FALSE])
data_523 <- mutate(data, normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS053018R.txt"), as.Date("2018-05-30")) %>% 
           mutate(Pos = ifelse(Sample.Name == "OX-II", 6, Pos),
                  Num = ifelse(Pos == 5, "S", "U"))
stdrat <- mean(data$cor1412he[data$Num == "S"])
data_530 <- mutate(data, normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS060618R.txt")) %>% 
  filter(Pos != 1,                           #remove spurious pos1 runs
         !(Pos == 3 & X13.12he > 0.011)) %>%     #remove solid OX-I fliers
                  mutate(Num = ifelse(Pos == 5, "S", "U"))
stdrat <- mean(data$cor1412he[data$Num == "S" & data$outlier == FALSE])
data_606 <- mutate(data, normFm = norm_gas(cor1412he, stdrat))

dbd <- rbind(data_523, data_530, data_606)

dbds <- sum_hgis(dbd) %>% 
  mutate(rec_num = case_when(str_detect(Sample.Name, "Live") ~ 101730,
                             Sample.Name == "OX-I" ~ 34148,
                             Sample.Name == "OX-II" ~ 34149,
                             str_starts(Sample.Name, "C1") ~ 83028)) %>% 
 left_join(select(std, rec_num, fm_consensus), by = "rec_num") %>% 
 mutate(fm_consensus = case_when(rec_num == 101730 ~ 1.0398,
                                 rec_num == 72446 ~ 0.0013,
                                 TRUE ~ fm_consensus),
        fm_diff = mean - fm_consensus)

dbds %>% 
  filter(Cur < 10) %>% 
  ggplot(aes(fm_consensus, fm_diff)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr),
                 position = position_dodge2(width = .1),
                 size = .5) +
  labs(title = "Closed inlet")
```

@@

```{r}
df %>% filter(fm_consensus < 0.1 &
              Cur > 2) %>% 
  ggplot(aes(Cur, mean)) +
  geom_errorbar(aes(ymin = mean - merr, ymax = mean + merr)) +
  geom_errorbarh(aes(xmin = Cur - Cur.sd, xmax = Cur + Cur.sd)) +
  geom_point(aes(color = wheel), size = 3) +
  labs(title = "Blanks",
       x = "Current (uA)",
       y = "Fraction modern") +
  theme(legend.position = c(0.85, 0.8),
        legend.background = element_rect(fill = "white", color = "black")) 
```
